---
title: "DCE Metrics Analysis, Scenario 1"
output: word_document
date: "2024-02-23"
---


## Analysis 
Once the survey  closed, the data was exported from Qualtrix and manually converted for to a format that could be used for analysis. 

#Scenario 1

```{r}
library(tidyr)
library(dplyr)
library(tidyverse)
library(survival)
#library(clogitLasso)
library(clogitL1)

##datasets:
#tmp2 = full dataset
#tmp3 = data with a measure selected from any combination of id and question
#tmp4 = data for only those who selected a meaure for each question

tmp2 <- readRDS("data/scenario1_full.rds")
tmp3 <- readRDS("data/scenario1_any.rds")
tmp4 <- readRDS("data/scenario1_responders.rds")

#number in each role by dataset
Role <- c("Librarian", "Systematic review methodologist", "Computer scientist", "Statistician", "Librarian and Systematic review methodologist", "Computer scientist and Systematic review methodologist")
table_roles <- readRDS("table_roles.rds")

table_roles <- as_tibble(cbind(Role,table_roles))

#write_csv(table_roles,"roles_table.csv")
```

#Definitions of charaacteristics and link to actual metrics

Characteristic 1: is sensitivity a ratio (1 = sensitivity	0 = true positives)
  
  sensitivity
  
  
Characteristic 2: Affected by prevalence (1 = affected by prevalence, 0 = not affected by prevalence)
  
  precision/positive predictive value
  
  negative predictive value
  
  correlation coefficient
  
  number needed to read
 
  F1 score
  
  F20 score
  
  accuracy
  
  


Characteristic 3: Designed with a valuation between sensitivty and workload	(1 = includes a beta; 0 = does not)
 
  F1 score
 
  F20 score
 
  accuracy
 
  
Characteristic 4: increases linearly with workload (1 = does, 0 = does not)
  
  false positives
  
  number needed to read
  
Characteristic 5: Includes TNs (1 = does, 0 = does not)

  specificity
  
  positive likelihood ratio
  
  negative predictive value
  
  correlation coefficient
  
  accuracy


#Basic model
```{r}

basic_model_all <- clogit(
  formula = selection ~ characteristic_1 + characteristic_2 +
     characteristic_3 + characteristic_4 + characteristic_5 + strata(id, question),
  data = tmp3)

basic_model_completers <- clogit(
  formula = selection ~ characteristic_1 + characteristic_2 +
     characteristic_3 + characteristic_4 + characteristic_5 + strata(id, question),
  data = tmp4)

summary(basic_model_completers)
round(exp(coef(basic_model_all)),2)
round(exp(confint(basic_model_all)),2)

performance::r2(basic_model_all)
extractAIC(basic_model_completers)

```
This basic conditional logistic regression model indicates that characteristics 1 and 4 may be guiding people's selection of metrics, with a preference for sensitivity over true positives and a preference for measures that increase linearly with burden (NNR or FP).

##Interactions
We then examined whether a person's preference for one characteristic affects their preference for another. For example if measures that incorporate true negatives are preferred, do respondents prefer them to also be dependent on prevalence (e.g., accuracy) or not (e.g., specificity)

#We explored the following interactions:
characteristic 1 (sensitivity) with all others. 

Because sensitivity is comparatively so important to systematic reviews, respondents might select  sensitivity regardless of the burden measure proposed.


characteristic 2 (affected by prevalence) interacted with 

  characteristic 3 (measures with both included accuracy and the F-score) 
  
  characteristic 4 (measures with both included NNR)
  
  characteristic 5 (measures with both included NPV, correlation coefficient, and accuracy)
  

characteristic 3 (Designed with a valuation between sensitivity and workload) interacted with 

  characteristic 4 (no measures included both)
  
  characteristic 5 (measures with both included accuracy)
  

characteristic 4 (measures with both included NNR) interacted with 

  characteristic 5 (no measures included both)
  

```{r}
tmp3$attribute_1 <- tmp3$characteristic_1
tmp3$attribute_2 <- tmp3$characteristic_2
tmp3$attribute_3 <- tmp3$characteristic_3
tmp3$attribute_4 <- tmp3$characteristic_4
tmp3$attribute_5 <- tmp3$characteristic_5

tmp4$attribute_1 <- tmp4$characteristic_1
tmp4$attribute_2 <- tmp4$characteristic_2
tmp4$attribute_3 <- tmp4$characteristic_3
tmp4$attribute_4 <- tmp4$characteristic_4
tmp4$attribute_5 <- tmp4$characteristic_5

```

##lasso responders

```{r}

#clogit and lasso to explore characteristics and their interactions: responders
set.seed(1234)

full_model_respond <-
  clogit(
  formula = selection ~ attribute_1 + 
                        attribute_2 +
                        attribute_3 + 
                        attribute_4 + 
                        attribute_5 +
                        attribute_1:attribute_2 +
                        attribute_1:attribute_3 +
                        attribute_1:attribute_4 +
                        attribute_1:attribute_5 +
                        attribute_2:attribute_3 +
                        attribute_2:attribute_4 +
                        attribute_2:attribute_5 +
                        attribute_3:attribute_5 +
    strata(id, question), data = tmp4)

full_model_any <-
  clogit(
  formula = selection ~ attribute_1 + 
                        attribute_2 +
                        attribute_3 + 
                        attribute_4 + 
                        attribute_5 +
                        attribute_1:attribute_2 +
                        attribute_1:attribute_3 +
                        attribute_1:attribute_4 +
                        attribute_1:attribute_5 +
                        attribute_2:attribute_3 +
                        attribute_2:attribute_4 +
                        attribute_2:attribute_5 +
                        attribute_3:attribute_5 +
    strata(id, question), data = tmp3)


#specify the response variable (selection) and the strata variables
x_resp <- model.matrix(full_model_respond)
y_resp <- as.numeric(tmp4$selection)
question_resp <- as.numeric(tmp4$question)
id_resp <- as.numeric(tmp4$id)

#specify the response variable (selection) and the strata variables
x_any <- model.matrix(full_model_any)
y_any <- as.numeric(tmp3$selection)
question_any <- as.numeric(tmp3$question)
id_any <- as.numeric(tmp3$id)


#run logit model
lasso_model_responders <- clogitL1(x = x_resp, y = y_resp, strata=as.numeric(strata(id_resp,question_resp)), numLambda=100,  minLambdaRatio=0.000001, switch=0, alpha=1)

lasso_model_any <- clogitL1(x = x_any, y = y_any, strata=as.numeric(strata(id_any,question_any)), numLambda=100,  minLambdaRatio=0.000001, switch=0, alpha=1)


plot(lasso_model_responders)
plot(lasso_model_any)
#summary(lasso_model)

cv_responders <- cv.clogitL1(lasso_model_responders,numFolds=10)
cv_any <- cv.clogitL1(lasso_model_any,numFolds=10)

plot(cv_responders)
plot(cv_any)

best_model_responders <- summary(cv_responders)
best_model_responders$lambda_minCV
best_model_any <- summary(cv_any)
best_model_any$lambda_minCV

variables <- c("attribute 1", "attribute 2", "attribute 3","attribute 4","attribute 5",
              "attributes 1 and 2",       
              "attributes 1 and 3","attributes 1 and 4",
              "attributes 1 and 5", "attributes 2 and 3", "attributes 2 and 4", "attributes 2 and 5",
              "attributes 3 and 5")
best_model_results_responders <- as_tibble(cbind(variables, round(exp(best_model_responders$beta_minCV),2), round(exp(best_model_responders$beta_minCV1se),2)))
best_model_results_responders <- best_model_results_responders %>%
  rename('OR, Min CV' = 'V2',  'OR Min CV 1 SE' = 'V3')

best_model_results_any <- as_tibble(cbind(variables, round(exp(best_model_any$beta_minCV),2), round(exp(best_model_any$beta_minCV1se),2)))
best_model_results_any <- best_model_results_any %>%
  rename('OR, Min CV' = 'V2',  'OR Min CV 1 SE' = 'V3')

best_model_results_responders
best_model_results_any

#Min CV 1 SE selects the simplest model with estimate CV within 1 standard deviation of the minimum cv.
```
##lasso all responses
```{r}
#clogit and lasso to explore characteristics and their interactions: all responses
set.seed(1234)

full_model <-
  clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 + 
                        #librarian + 
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_1:characteristic_4 +
                        characteristic_1:characteristic_5 +
                        #characteristic_2:characteristic_3 +
                        characteristic_2:characteristic_4 +
                        #characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
                        #characteristic_1:librarian +
                        #characteristic_2:librarian +
                        #characteristic_3:librarian +
                        #characteristic_4:librarian +
                        #characteristic_5:librarian +
    strata(id, question), data = tmp3)


#specify the response variable (selection) and the strata variables
x <- model.matrix(full_model)
y <- as.numeric(tmp3$selection)
question <- as.numeric(tmp3$question)
id <- as.numeric(tmp3$id)

#run logit model
lasso_model_all <- clogitL1(x = x, y = y, strata=as.numeric(strata(id,question)), numLambda=100,  minLambdaRatio=0.000001, switch=0, alpha=1)

plot(lasso_model_all)
#summary(lasso_model)

cv_all <- cv.clogitL1(lasso_model_all,numFolds=10)
plot(cv_all)
best_model_all <- summary(cv_all)
variables <- c("characteristic_1", "characteristic_2", "characteristic_3","characteristic_4","characteristic_5",
              "characteristic_1:characteristic_2",       
              "characteristic_1:characteristic_3","characteristic_1:characteristic_4",
              "characteristic_1:characteristic_5", "characteristic_2:characteristic_4",
              "characteristic_3:characteristic_5")
best_model_results_all <- as_tibble(cbind(variables, round(exp(best_model_all$beta_minCV),2), round(exp(best_model_all$beta_minCV1se),2)))
best_model_results_all <- best_model_results_all %>%
  rename('OR, Min CV' = 'V2',  'OR Min CV 1 SE' = 'V3')
best_model_results_all

#Min CV 1 SE selects the simplest model with estimate CV within 1 standard deviation of the minimum cv.


```
get rid of interactions, because they are = to 1 in tmp 4 and very close to 1 in tmp3:
1 & 4  
1 & 5
2 & 3
2 & 4

```{r}
#New clogit with only interactions that survived lasso regressions
#on tmp3 and tmp4

char_interact_model_responders <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 + 
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp4)

char_interact_model_all_responses <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 + 
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp3)

summary(char_interact_model_responders)
performance::r2(char_interact_model_responders)
extractAIC(char_interact_model_responders)
#create a table of results (magnitude and direction)
column_names <- c("Responders OR","Responders 95%CI low", "Responders 95%CI high","All responses OR","All responses 95%CI low", "All responses 95%CI high")
rows <- c("Characteristic 1: is sensitivity a ratio", "Characteristic 2: Affected by prevalence", "Characteristic 3: Designed with a valuation between sensitivty and workload","Characteristic 4: increases linearly with workload", "Characteristic 5: Includes TNs", "Interaction of characeristics 1 and 2", "Interaction of characeristics 1 and 3", "Interaction of characeristics 2 and 5", "Interaction of characeristics 3 and 5")

characteristics_table <- as_tibble(cbind(rows,
  round(exp(coef(char_interact_model_responders)),2), 
  round(exp(confint(char_interact_model_responders)),2),
  round(exp(coef(char_interact_model_all_responses)),2), 
  round(exp(confint(char_interact_model_all_responses)),2)
  ))
characteristics_table <- characteristics_table  %>%
  rename("Responders OR" = V2, "Responders 95%CI low"='2.5 %', "Responders 95%CI high"='97.5 %',"All responses OR"=V5,"All responses 95%CI low"=V6, "All responses 95%CI high"=V7)  %>%
  unite("Responders 95%CI", "Responders 95%CI low":"Responders 95%CI high", sep = '-', remove = TRUE) %>%
  unite("All responses 95%CI", "All responses 95%CI low":"All responses 95%CI high", sep = '-', remove = TRUE)
  

characteristics_table
#write_csv(characteristics_table,"results/characteristics_results.csv")
```


Finally, we looked to see whether these results differed by the respondent's role

  We were particularly interested in wether beaing a user of methods/tools (libraian or systematic reviewer) lead to having different preferences to being a producer (computer scientist), but given the very small sample of computer scientists who responded, we were unable to analyse this adequately. Thus we explored whether being a systematic reviewer lead to different preferences compared to all other roles, and whether being a librarian lead to different preferences compared to all other roles.

```{r}
#subset data to dataset for librarians and for SRs
tmp3_librarians <- tmp3[tmp3$librarian==1,]
tmp4_librarians <- tmp4[tmp4$librarian==1,] 
tmp3_sr <- tmp3[tmp3$systematic_reviewer==1,]
tmp4_sr <- tmp4[tmp4$systematic_reviewer==1,] 
tmp3_cs <- tmp3[tmp3$computer_scientist==1,]
tmp4_cs <- tmp4[tmp4$computer_scientist==1,]
tmp3_stat <- tmp3[tmp3$statistician==1,]
tmp4_stat <- tmp4[tmp4$statistician==1,]
```

```{r}
set.seed(1234)
#subset by role - use all data
lib_model <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 +
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_1:characteristic_4 +
                        characteristic_1:characteristic_5 +
                        characteristic_2:characteristic_3 +
                        characteristic_2:characteristic_4 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp3_librarians)

sr_model <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 +
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_1:characteristic_4 +
                        characteristic_1:characteristic_5 +
                        characteristic_2:characteristic_3 +
                        characteristic_2:characteristic_4 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp3_sr)

#specify the response variable (selection) and the strata variables librarians
x_lib <- model.matrix(lib_model)
y_lib <- as.numeric(tmp3_librarians$selection)
question_lib <- as.numeric(tmp3_librarians$question)
id_lib <- as.numeric(tmp3_librarians$id)

#specify the response variable (selection) and the strata variables sr
x_sr <- model.matrix(sr_model)
y_sr <- as.numeric(tmp3_sr$selection)
question_sr <- as.numeric(tmp3_sr$question)
id_sr <- as.numeric(tmp3_sr$id)

#run logit model
lasso_librarian <- clogitL1(x = x_lib, y = y_lib, strata=as.numeric(strata(id_lib,question_lib)), numLambda=100,  minLambdaRatio=0.000001, switch=0, alpha=1)

lasso_sr <- clogitL1(x = x_sr, y = y_sr, strata=as.numeric(strata(id_sr,question_sr)), numLambda=100,  minLambdaRatio=0.000001, switch=0, alpha=1)

plot(lasso_librarian)
plot(lasso_sr)

cv_lib <- cv.clogitL1(lasso_librarian,numFolds=10)
cv_sr <- cv.clogitL1(lasso_sr,numFolds=10)

plot(cv_lib)
plot(cv_sr)


best_model_lib <- summary(cv_lib)
best_model_sr <- summary(cv_sr)

variables <- c("characteristic_1", "characteristic_2", "characteristic_3","characteristic_4","characteristic_5",
              "characteristic_1:characteristic_2",       
              "characteristic_1:characteristic_3","characteristic_1:characteristic_4",
              "characteristic_1:characteristic_5", "characteristic_2:characteristic_3", "characteristic_2:characteristic_4", "characteristic_2:characteristic_5",
              "characteristic_3:characteristic_5")

results_lib <- as_tibble(cbind(variables, round(exp(coef(lib_model)),2), round(exp(best_model_lib$beta_minCV),2), round(exp(best_model_lib$beta_minCV1se),2)))
                         
results_lib <- results_lib %>%
  rename('Non-lasso' = 'V2', 'Min CV' = 'V3',  'OR Min CV 1 SE' = 'V4')

results_sr <- as_tibble((cbind(variables, round(exp(coef(sr_model)),2), round(exp(best_model_sr$beta_minCV),2), round(exp(best_model_sr$beta_minCV1se),2))))
results_sr <- results_sr %>%
  rename('Non-lasso' = 'V2', 'Min CV' = 'V3',  'OR Min CV 1 SE' = 'V4')

results_lib
results_sr


```
```{r}
#New clogit with only interactions that survived lasso regressions


char_interact_model_librarians <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 + 
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp3_librarians)

char_interact_model_sr <- clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        characteristic_3 + 
                        characteristic_4 + 
                        characteristic_5 + 
                        characteristic_1:characteristic_2 +
                        characteristic_1:characteristic_3 +
                        characteristic_2:characteristic_5 +
                        characteristic_3:characteristic_5 +
    strata(id, question), data = tmp3_sr)

summary(char_interact_model_librarians)
performance::r2(char_interact_model_librarians)
extractAIC(char_interact_model_librarians)

#create a table of results (magnitude and direction)
column_names <- c("Responders OR","Responders 95%CI low", "Responders 95%CI high","All responses OR","All responses 95%CI low", "All responses 95%CI high")
rows <- c("Characteristic 1: is sensitivity a ratio", "Characteristic 2: Affected by prevalence", "Characteristic 3: Designed with a valuation between sensitivty and workload","Characteristic 4: increases linearly with workload", "Characteristic 5: Includes TNs", "Interaction of characeristics 1 and 2", "Interaction of characeristics 1 and 3", "Interaction of characeristics 2 and 5", "Interaction of characeristics 3 and 5")

roles_table <- as_tibble(cbind(rows,
  round(exp(coef(char_interact_model_librarians)),2), 
  round(exp(confint(char_interact_model_librarians)),2),
  round(exp(coef(char_interact_model_sr)),2), 
  round(exp(confint(char_interact_model_sr)),2)
  ))
roles_table <- characteristics_table  %>%
  rename("Librarians OR" = V2, "Librarians 95%CI low"='2.5 %', "Librarians 95%CI high"='97.5 %',"SR OR"=V5,"SR 95%CI low"=V6, "SRs 95%CI high"=V7)  %>%
  unite("Librarians 95%CI", "Librarians 95%CI low":"Librarians 95%CI high", sep = '-', remove = TRUE) %>%
  unite("SR 95%CI", "SR 95%CI low":"SR 95%CI high", sep = '-', remove = TRUE)
  

roles_table
#write_csv(characteristics_table,"results/characteristics_results.csv")
```

```{r}
#logistic regression with librians
final_with_role_any <- clogit(
  formula = selection ~ characteristic_1 + 
    characteristic_2 +
    characteristic_3 + 
    characteristic_4 + 
    characteristic_5 + 
    librarian +
    characteristic_1:characteristic_2 +
    characteristic_1:characteristic_3 +
    characteristic_2:characteristic_5 +
    characteristic_3:characteristic_5 +
    characteristic_1:librarian +
    characteristic_2:librarian +
    characteristic_3:librarian +
    characteristic_4:librarian +
    characteristic_5:librarian +
    strata(id, question), data = tmp3)

final_with_role_complete <- clogit(
  formula = selection ~ characteristic_1 + 
    characteristic_2 +
    characteristic_3 + 
    characteristic_4 + 
    characteristic_5 + 
    librarian +
    characteristic_1:characteristic_2 +
    characteristic_1:characteristic_3 +
    characteristic_2:characteristic_5 +
    characteristic_3:characteristic_5 +
    characteristic_1:librarian +
    characteristic_2:librarian +
    characteristic_3:librarian +
    characteristic_4:librarian +
    characteristic_5:librarian +
    strata(id, question), data = tmp4)

summary(final_with_role_any)
performance::r2(final_with_role_any)
extractAIC(final_with_role_any)

summary(final_with_role_complete)
performance::r2(final_with_role_complete)
extractAIC(final_with_role_complete)

librows <- c("Characteristic 1: is sensitivity a ratio", "Characteristic 2: Affected by prevalence", "Characteristic 3: Designed with a valuation between sensitivty and workload","Characteristic 4: increases linearly with workload", "Characteristic 5: Includes TNs", "librarian", "Interaction of characeristics 1 and 2", "Interaction of characeristics 1 and 3", "Interaction of characeristics 2 and 5", "Interaction of characeristics 3 and 5",  "interaction of characteristic 1 and librarian", "interaction of characteristic 2 and librarian","interaction of characteristic 3 and librarian","interaction of characteristic 4 and librarian","interaction of characteristic 5 and librarian")

libcoef_any <- round(exp(coef(final_with_role_any)),2)
libci_any <- round(exp(confint(final_with_role_any)),2)

libcoef_complete <- round(exp(coef(final_with_role_complete)),2)
libci_complete <- round(exp(confint(final_with_role_complete)),2)

roles_table <- as_tibble(cbind(librows,libcoef_any,libci_any,libcoef_complete,libci_complete))
roles_table <- roles_table  %>%
  rename("OR any response" = libcoef_any, "OR completers" = libcoef_complete, "95%CI low"='2.5 %', "95%CI high"='97.5 %', "95%CI low c"=V6, "95%CI highc"=V7) %>%
  unite("95%CI", "95%CI low c":"95%CI high c", sep = '-', remove = TRUE)  
write_csv(roles_table,"libtable.csv")
```

```{r}
#LR test 

#Any response
library(lmtest)
likelihood_ratio_test <- lrtest(basic_model_completers, char_interact_model_all_responses)
likelihood_ratio_test

likelihood_ratio_test2 <- lrtest(basic_model_completers, final_with_role_complete)
likelihood_ratio_test2

```