---
title: "DCE Metrics Analysis, Scenario 2"
output: word_document
date: "2024-02-23"
---


## Analysis 
Once the survey  closed, the data was exported from Qualtrix and manually converted for to a format that could be used for analysis. 

#Scenario 1

```{r, echo=FALSE}
library(tidyr)
library(dplyr)
library(tidyverse)
library(survival)
library(clogitL1)

redo <- TRUE

if(redo){
scenario2 <- read.csv("data/scenario2.csv",colClasses = "character")
scenario2$characteristic_1 <- as.numeric(scenario2$characteristic_1)
scenario2$characteristic_2 <- as.numeric(scenario2$characteristic_2)
scenario2$characteristic_3 <- as.numeric(scenario2$characteristic_3)
scenario2$characteristic_4 <- as.numeric(scenario2$characteristic_4)
scenario2$characteristic_5 <- as.numeric(scenario2$characteristic_5)
scenario2$selection <- as.numeric(scenario2$selection)

tmp <- scenario2 %>% 
  as_tibble() %>%
  group_by(id, question) %>%
  # options should be arranged consistently 
  arrange(id, question, option) %>%
  filter(!str_starts(string = option,pattern = "equivalent")) %>%
  mutate(
    responded_A = (row_number() * selection) == 1,
  ) %>%
  ungroup()

#saveRDS(tmp, "scenario1_full.rds")
#clean the roles data 
#tmp <- readRDS("scenario1_full.rds")
contains_keyword <- function(role, keyword) {
  grepl(keyword, role, ignore.case = TRUE)
}

tmp_scen2 <- tmp %>%
  mutate(librarian = as.integer(contains_keyword(role, "librarian")),
         systematic_reviewer = as.integer(contains_keyword(role, "systematic|funder")),
         computer_scientist = as.integer(contains_keyword(role, "computer|software")),
         statistician = as.integer(!librarian & !systematic_reviewer & !computer_scientist),
         active_roles = case_when(
           librarian == 1 & systematic_reviewer == 1 ~ "systematic reviewer + librarian",
           systematic_reviewer == 1 & computer_scientist == 1 ~ "systematic reviewer + computer scientist",
           librarian == 1 ~ "librarian",
           systematic_reviewer == 1 ~ "systematic reviewer",
           computer_scientist == 1 ~ "computer scientist",
           statistician == 1 ~ "statistician"))

tmp_scen2$active_roles <- as.factor(tmp_scen2$active_roles)

tmp_scen2 <- tmp %>%
  mutate(librarian = as.integer(contains_keyword(role, "librarian")),
         systematic_reviewer = as.integer(contains_keyword(role, "systematic|funder")),
         computer_scientist = as.integer(contains_keyword(role, "computer|software")),
         statistician = as.integer(!librarian & !systematic_reviewer & !computer_scientist),
         lib_SR = case_when(
           librarian == 1 ~ 1,
           systematic_reviewer == 1 ~ 1,
           computer_scientist == 1 ~ 0,
           statistician == 1 ~ 0))


#write_csv(tmp2,"scenario2_full.csv")
#saveRDS(tmp_scen2,"scenario2_full.rds")
}
```

```{r}
##create datasets:
#tmp2 = full dataset
#tmp3 = data with a measure selected from any combination of id and question
#tmp4 = data for only those who selected a meaure for each question
if(redo){
tmp_scen2 <- readRDS("data/scenario2_full.rds")
tmp_scen2$question <- gsub("question_", "",tmp_scen2$question)
tmp_scen2$question <- as.numeric(tmp_scen2$question)

#tmp3 includes all results for which any person answered the question
tmp_scen3 <- tmp_scen2 %>% group_by(id, question) %>% mutate(noselect  = max(selection) == 0) %>% filter(!noselect) %>% ungroup 

tmp_scen3 <- tmp_scen3 %>% arrange(id, question, -selection)

#tmp 4 includes only results where the participant answered all questions
tmp_scen4 <- tmp_scen3 %>% group_by(id) %>% mutate(full_results  = sum(selection) == 6 ) %>% filter(full_results) %>% ungroup 

tmp_scen4 <- tmp_scen4 %>% arrange(id, question, selection)

#saveRDS(tmp_scen3,"scenario2_any.rds") 
saveRDS(tmp_scen4,"scenario2_responders.rds")
}
```

```{r}#
#tmp_scen2 <- readRDS("scenario2_full.rds")
#tmp_scen3 <- readRDS("scenario2_any.rds") 
tmp_scen4 <- readRDS("scenario2_responders.rds")

if(redo){
#create table of roles
for_table <-
tmp_scen2 %>% 
  group_by(id) %>% 
  filter(row_number()==1)

table_roles_all <- rbind(sum(for_table$librarian), sum(for_table$systematic_reviewer), sum(for_table$computer_scientist), sum(for_table$statistician),sum(for_table$librarian&for_table$systematic_reviewer),sum(for_table$computer_scientist&for_table$systematic_reviewer))

for_table <-
tmp_scen3 %>% 
  group_by(id) %>% 
  filter(row_number()==1)

table_roles_any <- rbind(sum(for_table$librarian), sum(for_table$systematic_reviewer), sum(for_table$computer_scientist), sum(for_table$statistician),sum(for_table$librarian&for_table$systematic_reviewer),sum(for_table$computer_scientist&for_table$systematic_reviewer))

for_table <-
tmp_scen4 %>% 
  group_by(id) %>% 
  filter(row_number()==1)

table_roles_responders <- rbind(sum(for_table$librarian), sum(for_table$systematic_reviewer), sum(for_table$computer_scientist), sum(for_table$statistician),sum(for_table$librarian&for_table$systematic_reviewer),sum(for_table$computer_scientist&for_table$systematic_reviewer))

table_roles <- cbind(table_roles_all, table_roles_any, table_roles_responders)
colnames(table_roles) <- c("N, all data", "N, any option chosen", "N, completers")
rownames(table_roles) <- c("librarian", "systematic reviewer", "computer scientist", "statistician", "librarian and systematic reviewer", "computer scientist and systematic reviewer")

#saveRDS(table_roles, "table_roles2.rds")

#table_roles <- readRDS("table_roles2.rds")

table_roles <- as_tibble(table_roles)
#write_csv(table_roles,"roles_table_scen2.csv")
table_roles
}
```


#Definitions of charaacteristics and link to actual metrics

Charateristic 1: is sensitivity a ratio (1 = sensitivity	0 = true positives)
    sensitivity, yield (sensitivity for the process)
Charateristic 2: Affected by prevalence (1 = affected by prevalence, 0 = not affected by prevalence)
    Work saved over sampling
Charateristic 3: Designed with a valuation between sensitivity and workload	(1 = includes a beta; 0 = does not)
    Combined yield and burden
    Work saved over sampling
Charateristic 4: increases linearly with workload (1 = does, 0 = does not) 
    Absolute screening reduction
    Burden/gain
Characteristic 5: Includes TNs (1 = does, 0 = does not) - All include TNs so this is not in model
    Absolute screening reduction
    Combined yield and burden
    Work saved over sampling
    Burden/gain

characteristics 3 and 4 are perfect inverse of each other. WHICH DO WE WANT?  

```{r}
#2 by 2 tables

if(redo){
# Create the first 2 by 2 table
table1 <- table(stats$characteristic_1, stats$selection)
table2 <- table(stats$characteristic_2, stats$selection)
table3 <- table(stats$characteristic_3, stats$selection)
table4 <- table(stats$characteristic_4, stats$selection)

df1 <- as.data.frame.table(table1)
names(df1)[1:2] <- c("characteristic_1", "selected")
df2 <- as.data.frame.table(table2)
names(df2)[1:2] <- c("characteristic_2", "selected")
df3 <- as.data.frame.table(table3)
names(df3)[1:2] <- c("characteristic_3", "selected")
df4 <- as.data.frame.table(table4)
names(df4)[1:2] <- c("characteristic_4", "selected")




librarians <- tmp_scen3[tmp_scen3$librarian==1,] 
sr <- tmp_scen3[tmp_scen3$systematic_reviewer==1,] 
cs <- tmp_scen3[tmp_scen3$computer_scientist==1,] 
stats <- tmp_scen3[tmp_scen3$statistician==1,] 

}

```
#Basic model
```{r}
basic_model <- clogit(
  formula = selection ~ characteristic_1 + characteristic_2 + characteristic_3 + strata(id, question),
  data = tmp_scen3)

round(exp(coef(basic_model)),2)
round(exp(confint(basic_model)),2)

#iteratively explored interactions = none that are not NA
performance::r2(basic_model)
extractAIC(basic_model)
```

This basic conditional logistic regression model indicates that people want sensitivity over true positives, they do not much care if the metric is affected by prevalence, and they do not like combined measures, but they do like models to increase linearly with workload.

Exploratory interaction analyses indicate that there is no interaction between characteristics.

Measures
```{r}
#clogit and lasso to explore characteristics and their interactions

full_model <-
  clogit(
  formula = selection ~ characteristic_1 + 
                        characteristic_2 +
                        #characteristic_3 + 
                        characteristic_4 + 
                        #librarian +
                        #systematic_reviewer + 
                        #characteristic_1:librarian +
                        #characteristic_2:librarian +
                        #characteristic_3:librarian +
                        #characteristic_4:librarian +
                        #characteristic_1:systematic_reviewer +
                        #characteristic_2:systematic_reviewer +
                        #characteristic_3:systematic_reviewer +
                        #characteristic_4:systematic_reviewer +
                        #characteristic_5 + 
                        #characteristic_1:characteristic_2 +
                        #characteristic_1:characteristic_3 +
                        #characteristic_1:characteristic_4 +
                        #characteristic_1:characteristic_5 +
                        #characteristic_2:characteristic_3 +
                        #characteristic_2:characteristic_4 +
                        #characteristic_2:characteristic_5 +
                        #characteristic_3:characteristic_5 +
    strata(id, question), data = tmp_scen4)

#No interactions among characteristics

```


Within 10011, people seemed to prefer absolute screening reduction (N=127, 58%) to burden/gain (93, 42%).